Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-16 paper/paper.tex
Compile graphs via PDFs

% \usepackage{showframe}
% \usepackage{refcheck}

\usepackage{microtype}                 % typographic perfection
\usepackage{complexity}                % \P, \NP etc
\usepackage{tikz}                      % For pretty pictures
\usepackage{amsmath}                   % \operatorname
\usepackage{amssymb}                   % \triangledown
\usepackage{hyperref}                  % clicky links
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
\usepackage{cite}                      % automatically sort mass cites
\usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page

\makeatletter\@ifpackageloaded{refcheck}{\newcommand{\citesforrefcheck}{\nocite{*}}}{\newcommand{\citesforrefcheck}{}}\makeatother

\usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing,
    patterns, matrix, shapes}

@@

\begin{figure}[tb]
    \centering
    \input{gen-graph-unconnected-cumulative}
    \vspace*{1em}

    \centering
    \input{gen-graph-unconnected-heatmap}
    \caption{The cumulative number of MCS instances solved in under a certain time: on the top, 33\%
        labelled graphs, and then unlabelled and undirected graphs. On the bottom, an
        instance-by-instance comparison of the clique model with the best CP model, with 33\%
        labelled graphs (with MAC) on the left, and unlabelled and undirected graphs (with FC) on
    the right.} \label{figure:unconnected-cumulative}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \input{gen-graph-connected-cumulative-cp}

    \vspace*{0.5em}
    \centering
    \input{gen-graph-connected-cp}
    \caption{On top, the cumulative number of MCCS instances solved in under a certain time using
        different CP techniques, for 33\% labelled (left) and unlabelled undirected (right) graphs.
    Below, instance-by-instance comparisons.}
        \label{figure:connected-cp}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \input{gen-graph-connected-cumulative}
    \vspace*{1em}

    \centering
    \input{gen-graph-connected-heatmap}
    \caption{The cumulative number of connected instances solved in under a certain time: on the
        top, 33\% labelled undirected graphs with up to 100 vertices, and then unlabelled
        and undirected graphs with up to 35 vertices. On the bottom, an instance-by-instance
        comparison of the association and CP Both approaches, with 33\% labelled graphs on the
        left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
\end{figure}

@@

\citesforrefcheck

>>>>

\usepackage{microtype}                 % typographic perfection
\usepackage{complexity}                % \P, \NP etc
\usepackage{tikz}                      % For pretty pictures
\usepackage{amsmath}                   % \operatorname
\usepackage{amssymb}                   % \triangledown
\usepackage{hyperref}                  % clicky links
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage[ruled,vlined]{algorithm2e} % algorithms (after cleverref!)
\usepackage{cite}                      % automatically sort mass cites
\usepackage[bottom]{footmisc}          % fix footnote + bottom figure on same page

\usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathreplacing,
    patterns, matrix, shapes, backgrounds}

@@

\begin{figure}[tb]
    \centering
    \includegraphics{gen-graph-unconnected-cumulative.pdf}
    \vspace*{1em}

    \centering
    \includegraphics{gen-graph-unconnected-heatmap.pdf}
    \caption{The cumulative number of MCS instances solved in under a certain time: on the top, 33\%
        labelled graphs, and then unlabelled and undirected graphs. On the bottom, an
        instance-by-instance comparison of the clique model with the best CP model, with 33\%
        labelled graphs (with MAC) on the left, and unlabelled and undirected graphs (with FC) on
    the right.} \label{figure:unconnected-cumulative}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics{gen-graph-connected-cumulative-cp.pdf}

    \vspace*{0.5em}
    \centering
    \includegraphics{gen-graph-connected-cp.pdf}
    \caption{On top, the cumulative number of MCCS instances solved in under a certain time using
        different CP techniques, for 33\% labelled (left) and unlabelled undirected (right) graphs.
    Below, instance-by-instance comparisons.}
        \label{figure:connected-cp}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics{gen-graph-connected-cumulative.pdf}
    \vspace*{1em}

    \centering
    \includegraphics{gen-graph-connected-heatmap.pdf}
    \caption{The cumulative number of connected instances solved in under a certain time: on the
        top, 33\% labelled undirected graphs with up to 100 vertices, and then unlabelled
        and undirected graphs with up to 35 vertices. On the bottom, an instance-by-instance
        comparison of the association and CP Both approaches, with 33\% labelled graphs on the
        left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
\end{figure}

@@
